Clustering: A pipeline to analyse time-course gene expression data

### 2019-03-22 scripts/03_clustering.Rmd
ENH Adding method to select number of clusters for the clustering

    - *Within cluster similarity as a function of the number of cluster* XXX
      GAP statistics
    - *Stability analysis*: this method assumes that the results of the
      clustering will be more stable for the "true" number of clusters than
      for other number of clusters.

>>>>

    - *Within cluster similarity as a function of the number of cluster* XXX
      Elbow method
    - *Silhouette method* 
    - *Stability analysis*: this method assumes that the results of the
      clustering will be more stable for the "true" number of clusters than
      for other number of clusters.

```{r}
possible_n_clusters = 5:20

```

### Elbow method

```{r elbow_method}

# function to compute total within-cluster sum of square 
within_cluster_sum_of_squares = function(n_cluster){
    return(moanin:::splines_kmeans(y, splines_model,
				   n_clusters=n_cluster, random_seed=42,
				   n_init=10)$tot.withinss)
}

i = 0
wss_values = list()
for(n_cluster in possible_n_clusters){
    wss_values[i] = within_cluster_sum_of_squares(n_cluster)
    i = i + 1
}

plot(possible_n_clusters, wss_values,
     type="b", pch=19, frame=FALSE, 
     xlab="Number of clusters K",
     ylab="Total within-clusters sum of squares")

```

### Average silhouette method

```{r average_silhouette_method}
# function to compute average silhouette for k clusters
average_silhoutte = function(n_cluster) {
    skmeans_results = moanin:::splines_kmeans(
	y, splines_model, n_clusters=n_cluster,
	random_seed=42, n_init=10)
    silhouette_results = cluster::silhouette(skmeans_results$cluster, dist(y))
    return(mean(silhouette_results[, 3]))
}

# extract the average silhoutte
average_silhoutte_values = list()
i = 1
for(n_cluster in possible_n_clusters){
    average_silhoutte_values[i] = average_silhoutte(n_cluster)
    i = i + 1
}

plot(possible_n_clusters, average_silhoutte_values,
     type="b", pch=19, frame=FALSE,
     xlab="Number of clusters K",
     ylab="Average Silhouettes")
```
